# Study Sites {-#sites}

This project will be conducted across four main study sites. Details about the locations were taken directly from current Forest management Plans that can be accessed [here](https://nrip.mnr.gov.on.ca/s/fmp-online?language=en_US).

```{r,echo=FALSE,warning=FALSE,message=FALSE}

library(mapview)
library(dplyr)
library(sf)
library(sp)
library(leaflet)

dog <- c("dog", 48.918, -90.230)
nipissing <- c("nipissing", 46.345, -79.456)
romeo <- c("romeo", 48.252, -81.692)
kenogami <- c("kenogami", 50.045, -86.793)

sites <- as.data.frame(rbind(dog,nipissing,romeo,kenogami))
names(sites) <- c("site","lat","lon")

sites <- sites %>%
    sf::st_as_sf(., coords = c("lon", "lat"))

st_crs(sites) <- st_crs(breweries)


mapview::mapview(sites, map.type = "Esri.WorldImagery")

```

## Romeo Malette {-#romeo}

The Romeo Malette Forest (Management Unit # 930) has been managed by RYAM Forest Management (formerly Tembec) since granted a Sustainable Forest License (SFL) No. 550398 by the MNRF on May 14, 2003. RYAM administers its forest management planning activities and operations from its office located in Timmins, Ontario.  MNRF administration for the forest is led by the Timmins District MNRFoffice. The Romeo Benefits from a comprehensive road network supporting forest management. 

```{r,echo=FALSE,warning=FALSE,message=FALSE}

m <- mapview::mapview(sites[3,],map.type = "Esri.WorldImagery")

coords <- c(romeo[3],
            romeo[2])

m@map %>% setView(coords[1], coords[2], zoom = 12)

```

## Kenogami Forest {-#kenogami}

The Kenogami Forest is located approximately 300 kilometres northeast of Thunder Bay. The Forest occupies an area of 1,977,684 hectares, of which 8.8% is water. Of the total forested area, less than 1% is patent land.  

```{r,echo=FALSE,warning=FALSE,message=FALSE}

m <- mapview::mapview(sites[4,],map.type = "Esri.WorldImagery")

coords <- c(kenogami[3],
            kenogami[2])

m@map %>% setView(coords[1], coords[2], zoom = 12)

```

## Dog River-Matawin Forest {-#dog}

The Forest covers 1,065,934 hectares of forested area, water and other non-forested areas. The distribution of lands and water across the various ownerships, as produced from the planning inventory,is as follows: 86.9% of the total management unit is under Crown ownership (84.9% in managed plus 2.0% in Crown Other),12.6% is patent land and 0.5% is other(federal land). 

```{r,echo=FALSE,warning=FALSE,message=FALSE}

m <- mapview::mapview(sites[1,],map.type = "Esri.WorldImagery")

coords <- c(dog[3],
            dog[2])

m@map %>% setView(coords[1], coords[2], zoom = 12)
```

## Nipissing Forest {-#nipissing}

The Nipissing Forest is administered and managed by Nipissing Forest Resource Management, Inc. (NFRM) under the authority of Sustainable Forest Licence (SFL) No. 542053. The company, NFRM, is owned by its shareholders: R. Fryer Forest Products Limited, Goulard Lumber (1971) Limited, Rayonier A.M. Canada G.P. (formerly Tembec Industries Inc.), Hec Clouthier and Sons Inc., and Georgian-Pacific (formerly Grant Forest Products Inc.).  The SFL, under the Crown Forest Sustainability Act, is administered by the Ontario Ministry of Natural Resources and Forestry, North Bay district office. It is well-accessed with a relatively extensive road network, and variation in the origin and degree of current activity.

```{r,echo=FALSE,warning=FALSE,message=FALSE}


m <- mapview::mapview(sites[2,],map.type = "Esri.WorldImagery")

coords <- c(nipissing[3],
            nipissing[2])

m@map %>% setView(coords[1], coords[2], zoom = 12)
```


