# Study Sites {-#sites}

This project will be conducted across four main study sites.

```{r,echo=FALSE,warning=FALSE,message=FALSE}

library(mapview)
library(dplyr)
library(sf)
library(sp)
library(leaflet)

boundary <- c("boundary", 48.751, -93.100)
nipissing <- c("nipissing", 46.345, -79.456)
romeo <- c("romeo", 48.252, -81.692)
ogoki <- c("ogoki", 50.899, -87.944)

sites <- as.data.frame(rbind(boundary,nipissing,romeo,ogoki))
names(sites) <- c("site","lat","lon")

sites <- sites %>%
    sf::st_as_sf(., coords = c("lon", "lat"))

st_crs(sites) <- st_crs(breweries)


mapview::mapview(sites, map.type = "Esri.WorldImagery")

```



## Boundary Waters Forest Management Area {-#boundary}

Boundary Waters Forest Management Area managed by Resolute Forest Products contains well mapped road networks interpreted from aerial imagery. 

```{r,echo=FALSE,warning=FALSE,message=FALSE}

m <- mapview::mapview(sites[1,],map.type = "Esri.WorldImagery")

coords <- c(boundary[3],
            boundary[2])

m@map %>% setView(coords[1], coords[2], zoom = 12)
```


## Nipissing Forest {-#nipissing}

(cooperative SFL Nipissing Forest Resource Management) which is well-accessed with a relatively extensive road network, and variation in the origin and degree of current activity 

```{r,echo=FALSE,warning=FALSE,message=FALSE}


m <- mapview::mapview(sites[2,],map.type = "Esri.WorldImagery")

coords <- c(nipissing[3],
            nipissing[2])

m@map %>% setView(coords[1], coords[2], zoom = 12)
```


## Romeo Malette {-#romeo}

(RYAM Forest Management) which has road networks supporting forestry and 

```{r,echo=FALSE,warning=FALSE,message=FALSE}

m <- mapview::mapview(sites[3,],map.type = "Esri.WorldImagery")

coords <- c(romeo[3],
            romeo[2])

m@map %>% setView(coords[1], coords[2], zoom = 12)

```

## Ogoki Forest {-#ogoki}

which is of high interest due to its location within key Caribou habitat. 


```{r,echo=FALSE,warning=FALSE,message=FALSE}

m <- mapview::mapview(sites[4,],map.type = "Esri.WorldImagery")

coords <- c(ogoki[3],
            ogoki[2])

m@map %>% setView(coords[1], coords[2], zoom = 12)

```

