# Study Sites {-#sites}

This project will be conducted across four main study sites. Details about the locations were taken directly from current Forest management Plans that can be accessed [here](https://nrip.mnr.gov.on.ca/s/fmp-online?language=en_US).

```{r,echo=FALSE,warning=FALSE,message=FALSE}

library(mapview)
library(dplyr)
library(sf)
library(sp)
library(leaflet)

dog <- c("Dog River-Matawin Forest", 48.918, -90.230)
nipissing <- c("Nipissing Forest", 46.345, -79.456)
romeo <- c("Romeo Malette Forest", 48.252, -81.692)
kenogami <- c("Kenogami Forest", 50.045, -86.793)

Sites <- as.data.frame(rbind(dog,nipissing,romeo,kenogami))
names(Sites) <- c("Site","lat","lon")

Sites <- Sites %>%
    sf::st_as_sf(., coords = c("lon", "lat"))

st_crs(Sites) <- st_crs(breweries)


mapview::mapview(Sites, map.type = "Esri.WorldImagery")

```

## Romeo Malette {-#romeo}

The Romeo Malette Forest (Management Unit # 930) has been managed by RYAM Forest Management (formerly Tembec) since granted a Sustainable Forest License (SFL) No. 550398 by the MNRF on May 14, 2003. RYAM administers its forest management planning activities and operations from its office located in Timmins, Ontario.  MNRF administration for the forest is led by the Timmins District MNRFoffice. The Romeo Benefits from a comprehensive road network supporting forest management. 

```{r,echo=FALSE,warning=FALSE,message=FALSE}

m <- mapview::mapview(Sites[3,],map.type = "Esri.WorldImagery")

coords <- c(romeo[3],
            romeo[2])

m@map %>% setView(coords[1], coords[2], zoom = 12)

```

<br>
**Data Collection**

**SPL:** 

* Flow by: Fugro USA Land, 
* Inc. Project name: OMNR_YR1 z17.
* Date: June 2018

**Roads:**

* Ministry of Natural Resources and Forestry (MNRF) road data 
* Full roads network including road attributes, descriptions of which are accessed [here](https://www.sdc.gov.on.ca/sites/MNRF-PublicDocs/EN/CMID/MNR%20Road%20Segment%20-%20Data%20Description.pdf).

**Additional Data:** Fire extent 2021, Lakes and rivers, Land ownership, Plot inventory data, and Polygon inventory


## Kenogami Forest {-#kenogami}

The Kenogami Forest is located approximately 300 kilometres northeast of Thunder Bay. The Forest occupies an area of 1,977,684 hectares, of which 8.8% is water. Of the total forested area, less than 1% is patent land.  

```{r,echo=FALSE,warning=FALSE,message=FALSE}

m <- mapview::mapview(Sites[4,],map.type = "Esri.WorldImagery")

coords <- c(kenogami[3],
            kenogami[2])

m@map %>% setView(coords[1], coords[2], zoom = 12)

```

<br>
**Data Collection**

**SPL:** NA

**Roads:**

* Ministry of Natural Resources and Forestry (MNRF) road data 
* Full roads network including road attributes, descriptions of which are accessed [here](https://www.sdc.gov.on.ca/sites/MNRF-PublicDocs/EN/CMID/MNR%20Road%20Segment%20-%20Data%20Description.pdf).

**Additional Data:** Fire extent 2021, Lakes and rivers, Land ownership, Plot inventory data, and Polygon inventory

## Dog River-Matawin Forest {-#dog}

The Forest covers 1,065,934 hectares of forested area, water and other non-forested areas. The distribution of lands and water across the various ownerships, as produced from the planning inventory,is as follows: 86.9% of the total management unit is under Crown ownership (84.9% in managed plus 2.0% in Crown Other),12.6% is patent land and 0.5% is other(federal land). 

```{r,echo=FALSE,warning=FALSE,message=FALSE}

m <- mapview::mapview(Sites[1,],map.type = "Esri.WorldImagery")

coords <- c(dog[3],
            dog[2])

m@map %>% setView(coords[1], coords[2], zoom = 12)
```

<br>
**Data Collection**

**SPL:**

* Flow by: Leica Geosystems Inc.
* Project name: OMNR_SPL100
* Date: June 2019

**Roads:**

* Ministry of Natural Resources and Forestry (MNRF) road data 
* Full roads network including road attributes, descriptions of which are accessed [here](https://www.sdc.gov.on.ca/sites/MNRF-PublicDocs/EN/CMID/MNR%20Road%20Segment%20-%20Data%20Description.pdf).
* Resolute Forest Products road data.


**Additional Data:** Fire extent 2021, Lakes and rivers, Land ownership, Plot inventory data, and Polygon inventory

## Nipissing Forest {-#nipissing}

The Nipissing Forest is administered and managed by Nipissing Forest Resource Management, Inc. (NFRM) under the authority of Sustainable Forest Licence (SFL) No. 542053. The company, NFRM, is owned by its shareholders: R. Fryer Forest Products Limited, Goulard Lumber (1971) Limited, Rayonier A.M. Canada G.P. (formerly Tembec Industries Inc.), Hec Clouthier and Sons Inc., and Georgian-Pacific (formerly Grant Forest Products Inc.).  The SFL, under the Crown Forest Sustainability Act, is administered by the Ontario Ministry of Natural Resources and Forestry, North Bay district office. It is well-accessed with a relatively extensive road network, and variation in the origin and degree of current activity.

```{r,echo=FALSE,warning=FALSE,message=FALSE}


m <- mapview::mapview(Sites[2,],map.type = "Esri.WorldImagery")

coords <- c(nipissing[3],
            nipissing[2])

m@map %>% setView(coords[1], coords[2], zoom = 12)
```
<br>
**Data Collection**

**SPL:**

* Flow by: Leica Geosystems
* Project name: OMNR
* Date: June 2019

**Roads:**

* Ministry of Natural Resources and Forestry (MNRF) road data 
* Full roads network including road attributes, descriptions of which are accessed [here](https://www.sdc.gov.on.ca/sites/MNRF-PublicDocs/EN/CMID/MNR%20Road%20Segment%20-%20Data%20Description.pdf).

**Additional Data:** Fire extent 2021, Lakes and rivers, Land ownership, Plot inventory data, and Polygon inventory
